An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/motiv.tex
config: small updates on motiv

\para{Example~4: Singular Value Errors} 
A common error is that a value is set too high or too low.
For example, a parameter relating to memory might be too large,
exhausting the RAM and causing extreme slowness or even a crash. 
Consider the following real-world misconfiguration file \cite{singleValue}: the
user was experiencing the ``My SQL Server has gone away" error.  
She had the following line in her configuration file.

>>>>

\para{Example~4: Singular Value Errors} 
Many system performance problems are caused by 
error that a value is set too high or too low.
For example, a parameter relating to memory might be too large,
exhausting the RAM and causing extreme slowness or even a crash. 
Consider the following real-world misconfiguration file%
~\cite{singleValue}: a user was experiencing the ``My SQL Server 
has gone away" error.  
She had the following line in her configuration file.
